### 2019-03-21 1_introduction.tex
Edit intro.

One approach to answering this question has focused around the
development of \emph{proxy-} or \emph{mini-apps}. So called because
they embody the logic of a larger application, but in reduced form,
mini-apps are popular because they can provide insight without
incurring the costly expense of developing a full-blown application
code. However, despite the name, mini-apps still requite significant
investment to develop, especially to a level of quality need to reach
a publishable state. In many cases, the effort to tune for performance
exceeds the effort to develop the mini-app in the first place. This
can be exacerbated if the system in question is undergoing concurrent
development. As a result, implementations of mini-apps, though
well-intentioned, often do not reach a level of maturity required to
perform a broad comparison between systems, and as a result there are
very few comparative studies involving multiple programming systems
that reach publication.

@@

To resolve the methodological issue, we introduce a new metric called
\emph{minimum effective task granularity} (METG). Intuitively, METG is
the smallest task granularity which can be executed while maintaining
a given level of computational efficiency (e.g., as measured by the
percentage of peak FLOPS achieved). METG captures the essence of what
is important in a weak or strong scaling study: that is, the behavior
at the limit of scalability. For weak scaling, METG corresponds
directly to the smallest problem size that can be weak scaled with a
given level of efficiency. For strong scaling, METG can be used to
compute the point at which strong scaling can be expected to tail
off. In either case, METG is a useful, intuitive measure as it
encapsulates the task granularity at which systems can be relied on to
execute efficiently. As a rule of thumb, as long as an application's
average task granularity exceeds the METG, the application should
execute efficiently.

@@

But there is a deeper issue with the use of empty tasks. In all
realistic scenarios, runtime systems must share resources with the
application, either explicitly by e.g., allocating cores for runtime
use, or implicitly by sharing a time slice on the same cores used for
application tasks, and other resources such as memory bandwidth and
processor cache capacity. The use of empty tasks makes the application
share of these resources appear to be zero, which permits usage by the
runtime system to be unconstrained. How then is anyone supposed to
determine what resource usage to consider reasonable on the part of
the runtime system? Only by requiring the application usage of
resources to meet a certain minimum level, as in METG, can we ensure
that runtime system resource usage is constrained to realistic levels.

>>>>

One approach to answering this question has focused around the
development of \emph{proxy-} or \emph{mini-apps}. So called because
they embody the logic of a larger application, but in reduced form,
mini-apps are popular because they can provide insight without
incurring the costly expense of developing a full-blown application
code. However, despite the name, mini-apps still requite significant
investment to develop, especially to a level of quality needed to reach
a publishable state. In many cases, the effort to tune for performance
exceeds the effort to develop the mini-app in the first place. This
can be exacerbated if the system in question is undergoing concurrent
development. As a result, implementations of mini-apps, though
well-intentioned, often do not reach a level of maturity required to
perform a broad comparison between systems, and as a result there are
few comparative studies involving multiple programming systems
that reach publication.

@@

To resolve the methodological issue, we introduce a new metric called
\emph{minimum effective task granularity} (METG). Intuitively, METG is
the smallest task granularity which can be executed while maintaining
a given level of computational efficiency (e.g., as measured by the
percentage of peak FLOPS achieved). METG captures the essence of what
is important in a weak or strong scaling study: that is, the behavior
at the limit of scalability. For weak scaling, METG corresponds
directly to the smallest problem size that can be weak scaled with a
given level of efficiency. For strong scaling, METG can be used to
compute the scale at which performance can be expected to dip below
that level of efficiency. In either case, METG is a useful, intuitive
measure as it
encapsulates the task granularity at which systems can be relied on to
execute efficiently. As a rule of thumb, as long as an application's
average task granularity exceeds the METG, the application should
execute efficiently.

@@

But there is a deeper issue with the use of empty tasks. In all
realistic scenarios, runtime systems must share resources with the
application, either explicitly by e.g., allocating cores for runtime
use, or implicitly by sharing a time slice on the same cores used for
application tasks, and other resources such as memory bandwidth and
processor cache capacity. The use of empty tasks makes the application
share of these resources appear to be zero, which permits usage by the
runtime system to be unconstrained. How then is one supposed to
determine what resource usage to consider reasonable on the part of
the runtime system? Only by requiring the application usage of
resources to meet a certain minimum level, as in METG, can we ensure
that runtime system resource usage is constrained to realistic levels.
